### 2016-09-30 architecture.tex
Reword
Clearer wording

\subsection{The Core}
\label{sec:core}
A computer algebra system stores mathematical expressions as data
structures.  For example, the mathematical expression $x + y$ is represented as
a tree with three nodes, $+$, $x$, and $y$, where $x$ and $y$ are ordered
children of $+$.  As users manipulate
mathematical expressions with traditional mathematical syntax, the CAS
manipulates the underlying data structures.  Automated optimizations and
computations such as integration, simplification, etc.\ are all functions that
consume and produce expression trees.

@@

Importantly, SymPy expressions are immutable. This simplifies the design of
SymPy by allowing expression interning. It also enables expressions to be
hashed, which is used to implement caching in SymPy.

>>>>

\subsection{The Core}
\label{sec:core}
A computer algebra system stores mathematical expressions as data structures.
For example, the mathematical expression $x + y$ is represented as a tree with
three nodes, $+$, $x$, and $y$, where $x$ and $y$ are ordered children of $+$.
As users manipulate mathematical expressions with traditional mathematical
syntax, the CAS manipulates the underlying data structures. Symbolic
computations such as integration, simplification, etc.\ are all functions that
consume and produce expression trees.

@@

Another important property of SymPy expressions is that they are immutable.
This simplifies the design of SymPy by allowing expression interning. It also
enables expressions to be hashed, which is used to implement caching in SymPy.
